# Vietnamese {#viet}

This section is dedicated to Vietnamese recipes.

## Soups

Bun bo hue

Hu thieu

Pho

Bo kho

Pickled mustard green soup

Rau muon


## Noodles and Rice

Bun with calamari and fried shrimp.

Bun thit nuong with eggrolls.

Fried Rice

## Banh

Banh Bao

Banh Xeo

Banh mi


## Meats

Lemongrass pork

Carmel chicken

Sweet and sour pork

Little pork


## Extras

Pate

Pickles

Eggrolls

Spring rolls with chili-lemongrass tofu

Shrimp and omelet springrolls

Peanut sauce

Special fish sauce

Pickled mustard greens

```{r nice-fig, fig.cap='Here is a nice figure!', out.width='80%', fig.asp=.75, fig.align='center'}
par(mar = c(4, 4, .1, .1))
plot(pressure, type = 'b', pch = 19)
```

Reference a figure by its code chunk label with the `fig:` prefix, e.g., see Figure \@ref(fig:nice-fig). Similarly, you can reference tables generated from `knitr::kable()`, e.g., see Table \@ref(tab:nice-tab).

```{r nice-tab, tidy=FALSE}
knitr::kable(
  head(iris, 20), caption = 'Here is a nice table!',
  booktabs = TRUE
)
```

You can write citations, too. For example, we are using the **bookdown** package [@R-bookdown] in this sample book, which was built on top of R Markdown and **knitr** [@xie2015].
